Coupling PDEs on 3D-1D domains with Lagrange multipliers

### 2019-07-22 3d1d_coupled_LM.tex

% SIAM Article Template
\documentclass[r]{siamart171218}
% Packages and macros go here
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumitem}  
\usepackage{epstopdf}
\usepackage{stmaryrd}

@@

\def\ud{u_{\odot}}
\def\vd{v_{\odot}}
\def\ld{\lambda_{\odot}}
\def\md{\mu_{\odot}}
\def\lld{l_{\odot}}
\def\uf{u_{\ominus}}
\def\up{u_{\oplus}}
\def\eps{\epsilon}
\def\nn{\boldsymbol n}
\def\rr{\boldsymbol r}
\def\RR{\boldsymbol R}
\def\kk{\boldsymbol k}
\def\ss{\boldsymbol s}
\def\uu{\boldsymbol u}
\def\vv{\boldsymbol v}
\def\xx{\boldsymbol x}
\def\bu{\overline{u}}
\def\bv{\overline{v}}
\def\tu{\widetilde{u}}
\def\tv{\widetilde{v}}
\def\TT{\boldsymbol T}
\def\NN{\boldsymbol N}
\def\BB{\boldsymbol B}
\def\ttu{\widetilde{\widetilde{u}}}
\def\ttv{\widetilde{\widetilde{v}}}
\def\cv{\check{v}}
\def\mesh{{\cal T}^h}
\def\ball{{\cal B}}
\def\R{\mathbb{R}}
\def\D{\mathcal{D}}
\def\DD{\partial\mathcal{D}}
\def\trace{\overline{\mathcal{R}}}
\def\ext{\mathcal{E}}
\def\ide{\mathcal{I}}
\def\ii{\hat{\imath}}
\newcommand{\avrd}[1]{\overline{\overline{#1}}}
\newcommand{\avrc}[1]{\overline{#1}}
\newcommand{\refe}[1]{{#1}_{\mathrm{ref}}}

@@

Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set. Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega_\ominus}$ be the complementary set of the cylinder. We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Omega_\ominus$. We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$. We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively. 
%In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. 
We also assume that $\Omega_\ominus$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Omega_\ominus$, while the upper and lower side faces of $\Omega_\ominus$ belong to $\partial\Omega$. We refer to Figure \ref{fig1} for an illustration of the notation.

@@

The objective of this work is to derive and alalyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$. This new problem setting will be called the \emph{reduced} problem. Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.
For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
\begin{equation*}
\int_{\Omega_\ominus} w d\omega 
= \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
= \int_\Lambda |\mathcal{D}|\avrd{w} ds\,,
\quad
\int_{\Gamma} w d\sigma 
= \int_\Lambda \int_{\partial\mathcal{D}} w d\gamma ds
= \int_\Lambda  |\partial \mathcal{D}| \avrc{w} ds\,,
\end{equation*}
where $\avrd{w}, \ \avrc{w}$ denote the following mean values respectively,
\begin{equation*}
\avrd{w} = |\mathcal{D}|^{-1} \int_{\mathcal{D}} w d\sigma\,,
\quad
\avrc{w} = |\partial\mathcal{D}|^{-1} \int_{\partial\mathcal{D}} w d\gamma\,.
\end{equation*}

@@

Using the averaging tools for the model reduction approach, we end up with two different formulations of a reduced problem
for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
%In the reduced problem the multiplier assumes the following interpretation,
%\begin{equation*}
%L = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \nabla \uf \cdot \nn_\ominus
%   = - \frac{1}{|\partial{\cal D}|} \int_{\partial{\cal D}} \lambda \,.
%\end{equation*}

%We consider two alternative formulations.
The scope of this work is to compare them, 
with the aim to determine which is the most suitable as a computational model based on 3D-1D coupled PDEs.

@@

We apply the averaging technique to equation \eqref{eq:dirneu2}. In particular, we consider an arbitrary portion $\mathcal{P}$ of the cylinder $\Omega_\ominus$, with lateral surface $\Gamma _{\mathcal{P}}$ and bounded by two perpendicular sections to $\Lambda$, namely $\mathcal{D}(s_1), \ \mathcal{D}(s_2)$ with $s_1<s_2$. We have,
\begin{multline*}
\int_{\mathcal{P}} -\Delta \uf + \uf d\omega =
-\int_{\partial \mathcal{P}} \nabla \uf \cdot \nn_{\ominus} \, d\sigma  + \int_{\mathcal{P}}\uf d\omega=
\\
 \int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma -  \int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma +\int_{\mathcal{P}}\uf d\omega
\end{multline*}
By the fundamental theorem of integral calculus combined with the Reynolds transport Theorem, 
%where $d_s |\partial\mathcal{D}(s)|$ is the rate at which the cross section changes size,
being $\nu$ the normal component of the velocity of the boundary, 
we have,
%\begin{multline*}
%-\int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma +  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma 
%= \int_{s_1}^{s_2} d_s \int_{\mathcal{D}(s)}  \partial_s \uf d\sigma ds
%\\
%= \int_{s_1}^{s_2} \int_{\mathcal{D}(s)} \partial^2_{ss} \uf d\sigma ds + \int_{s_1}^{s_2} \int_{\partial\mathcal{D}(s)} \nu \partial_s \uf d\gamma ds
%\\
%= \int_{s_1}^{s_2} \left[ |\mathcal{D}(s)| d^2_{ss} \avrd{u}_{\ominus}  + |\partial\mathcal{D}(s)| \nu  d_s \avrc{u}_{\ominus} \right] ds.
%\end{multline*}

@@

 (d_s \ud, d_s \ud)_{\Lambda,|\mathcal{D}|} 

@@

\subsubsection*{Topological model reduction of the problem on $\Omega_{\oplus}$}
We focus here on the subproblem of \eqref{eq:dirneu1} related to $\Omega_{\oplus}$.
We multiply both sides of \eqref{eq:dirneu1} by a test function $v\in H^1_0(\Omega)$ and integrate on $\Omega_\oplus$. Integrating by parts and using boundary and interface conditions, we obtain
\begin{equation*}
\begin{split}
\int_{\Omega _{\oplus}}fv\,d\omega&=
\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int _{\partial \Omega _{\oplus}}\nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v
\\
&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega -\int_{\Gamma} \nabla \up \cdot \nn_{\oplus} v + \int_{\Omega_{\oplus}} \up v
\\
&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega +\int_{\Gamma} \lambda v + \int_{\Omega_{\oplus}} \up v.
\end{split}
\end{equation*} 
Then, we make the following modelling assumptions:
\begin{description}
\item[A2] we identify the domain $\Omega_{\oplus}$ with the entire $\Omega$, 
and we correspondingly omit the subscript $\oplus$ to the functions defined on $\Omega_{\oplus}$,
namely
\begin{equation*}
\int_{\Omega_{\oplus}} u_\oplus\, d\omega \simeq \int_{\Omega} u\, d\omega\,.
\end{equation*}
\end{description}
Therefore, we obtain 
\begin{equation*}
(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\lambda, v)_{\Gamma}  =(f,v)_{\Omega}
\end{equation*}
and combining with \eqref{eq:1Ddirneu_weak} we obtain the first formulation of the reduced problem.

\subsubsection*{Problem 1 (3D-1D-3D)}
Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$. The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$, such that
\begin{subequations}\label{eq:problem1}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+ \langle T v  - \mathcal{U}_E \vd, \lambda \rangle_\Gamma
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
\\
&   \langle T u - \mathcal{U}_E \ud , \mu \rangle_\Gamma = 0
\quad \forall \mu \in H^{-\frac12}(\Gamma)\,.
\end{align}
\end{subequations}
Here, $T:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator on $\Gamma$ and $\mathcal{U}_E: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$. The idea is then to couple a 3D PDE with a 1D one, using a Lagrange multiplier space defined on a 2D surface that surrounds the 1D manifold.\\

%Here, $\Pi_1: H^1_0(\Omega) \rightarrow H^{\frac12}_{00}(\Gamma)$
%and $\Pi_2: H^1_0(\Lambda) \rightarrow H^{\frac12}_{00}(\Gamma)$
%and we remark that $\Sigma$ may be considered as a virtual surface
%not necessarily of the same size as the underlying physical structure that is modeled.  
%The $\Pi_1$ and $\Pi_2$ operators may be defined in terms of the averaging operators above, but may also be realized in terms of e.g. Green functions (I don't know if this is a good idea). Furthermore,  $\Gamma$ may be discretized in terms of facets neighboring $\Lambda$ and may as such not be represented as a separate structure in the implementation.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-3D to a 3D-1D-1D formulation. 
To this purpose, let us write the lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
\begin{equation*}
\lambda=\avrc{\lambda}+\tilde{\lambda}, \qquad v=\avrc{v}+\tilde{v},
\quad \text{on} \ \partial\mathcal{D}(s)\,,
\end{equation*}
where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
Therefore, using the coordinates system $(r,s,t)$ on $\Gamma$, we have
\begin{equation*}
\int_{\Gamma}\lambda v\, d\sigma
=\int _{\Lambda}  \int_{\partial\mathcal{D}(s)} (\avrc{\lambda}+\tilde{\lambda})(\avrc{v}+\tilde{v})d\gamma ds
= \int_{\Lambda}|\partial\mathcal{D}(s)| \avrc{\lambda}\avrc{v}\,ds+\int_{\Lambda}  \int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v}d\gamma ds\,.
\end{equation*}

@@

\subsection{Problem 2 (3D-1D-1D)}
Let $\langle \cdot , \cdot \rangle_\Lambda$ denote the duality pairing between 
$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
\begin{subequations}\label{eq:problem2}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+  \langle \avrc{T v} - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)
\\
&   \langle \avrc{T u} -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
\quad \forall \md \in H^{-\frac12}(\Lambda)\,.
\end{align}
\end{subequations}
We notice that all the integrals of the reduced problem are well defined because $u,v \in H^1_0(\Omega)$, 
$Tu, \ Tv \in H^\frac12_{00}(\Gamma)$ and thus $\avrc{Tu},\avrc{Tv} \in H^\frac12_{00}(\Lambda)$, as shown in the following lemma.
%More precisely, $\Pi_1 : H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda$ such that
%$\Pi_1 u = \avrc{(u|_\Gamma)}$ is the combination between the trace on $\Gamma$ and the average on $\partial{\cal D}$.
%The operator $\Pi_2: H^1_0(\Lambda) \rightarrow H^\frac12_{00}(\Lambda)$ is the injection form $H^1_0(\Lambda)$ and $H^\frac12_{00}(\Lambda)$.

\begin{lemma}\label{lemma:H12norm}
{\color{red}TO DO: generalize to not uniform $\DD$} 
When $\Gamma$ is a cylinder, if $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}\in H_{00}^{\frac 12}(\Lambda)$. Moreover, if $u\in H^{\frac 12}_{00}(\Gamma)$ is constant on each cross section, namely $u(s,\theta)=u(s)$, then 
\begin{equation*}
\|u\|_{H^{\frac 12}_{00}(\Gamma)}=2\pi R \|u\|_{H^{\frac 12}_{00}(\Lambda)}.
\end{equation*}
\end{lemma}
\begin{proof}
Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $\Lambda$. In particular,
\begin{align*}
\phi _{ij}(s,\theta)=sin (i\pi s)\left( cos(j\theta)+ sin(j\theta) \right),\\
\rho_{ij}=i\pi ^2+\frac{j^2}{R^2},\\
\phi _{i}(s)=sin (i\pi s),\\
\rho _i = i\pi ^2.
\end{align*}
It is easy to verify that 
\begin{eqnarray}
\label{null_int_eigenf}
\int_0^{2\pi} \phi _{ij}(s,\theta)=0 \quad \forall j>0, \forall i \\
\label{nonull_int_eigenf}
\int_0^{2\pi} \phi _{ij}(s,\theta)= 2\pi R \, \sin(i \pi s) \quad \mbox{if } j=0, \forall i  .\\
\end{eqnarray}
Moreover we recall that $\phi_{i,j}(s,\theta)$ and $\phi _i(s)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(\Lambda)$ respectively. Therefore,
\begin{multline*}
\avrc{u}(s)=\frac{1}{2\pi R}\int_0^{2\pi} u(s,\theta)R\, d\theta
= \frac{1}{2\pi R}\int_0^{2\pi} \sum_{i,j} a_{i,j} \phi_{i,j}(s,\theta) R\, d\theta
\\= \frac{1}{2\pi R}\sum_{i,j} a_{i,j}\int_0^{2\pi}  \phi_{i,j}(s,\theta) R\, d\theta
=  \sum_{i} a_{i,0} \phi_{i}(s).
\end{multline*}
From \cite[Lemma 4.11]{chandler2015interpolation} we have
\begin{equation}\label{H12norm_Gamma}
\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
\text{ with }
a_{ij}=\int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds.
\end{equation}
and 
\begin{equation*}
\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
\text{ with }
\avrc{a}_i=\int _0^1 \avrc{u}(s )\phi_{i}(s) ds.
\end{equation*}

>>>>

% SIAM Article Template
\documentclass[r]{siamart171218}
% Packages and macros go here
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{array}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{float}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumitem}  
\usepackage{epstopdf}
\usepackage{stmaryrd}
\usepackage{tikz, subfigure}

@@

\def\ud{u_{\odot}}
\def\vd{v_{\odot}}
\def\ld{\lambda_{\odot}}
\def\md{\mu_{\odot}}
\def\lld{l_{\odot}}
\def\uf{u_{\ominus}}
\def\up{u_{\oplus}}
\def\eps{\epsilon}
\def\nn{\boldsymbol n}
\def\rr{\boldsymbol r}
\def\RR{\boldsymbol R}
\def\kk{\boldsymbol k}
\def\ss{\boldsymbol s}
\def\uu{\boldsymbol u}
\def\vv{\boldsymbol v}
\def\xx{\boldsymbol x}
\def\bu{\overline{u}}
\def\bv{\overline{v}}
\def\tu{\widetilde{u}}
\def\tv{\widetilde{v}}
\def\TT{\boldsymbol T}
\def\NN{\boldsymbol N}
\def\BB{\boldsymbol B}
\def\ttu{\widetilde{\widetilde{u}}}
\def\ttv{\widetilde{\widetilde{v}}}
\def\cv{\check{v}}
\def\mesh{{\cal T}^h}
\def\ball{{\cal B}}
\def\R{\mathbb{R}}
\def\D{\mathcal{D}}
\def\DD{\partial\mathcal{D}}
\def\trace{{\mathcal{T}_\Gamma}}
\def\mtrace{{\overline{\mathcal{T}}_\Lambda}}
\def\ext{\mathcal{E}_\Gamma}
\def\ide{\mathcal{I}}
\def\ii{\hat{\imath}}
\newcommand{\avrd}[1]{\overline{\overline{#1}}}
\newcommand{\avrc}[1]{\overline{#1}}
\newcommand{\refe}[1]{{#1}_{\mathrm{ref}}}

@@

Let $\Omega \subset \mathbb{R}^3$ be a bounded, convex open set. Let $\Omega_\ominus$ be a generalized cylinder embedded into $\Omega$ and be $\Omega_\oplus = \Omega \setminus \overline{\Omega}_\ominus$ be the complementary set of the cylinder. We also introduce the set $\Lambda$, a 1D manifold that is the centerline of $\Omega_\ominus$. We define the arc-length coordinate along $\Lambda$, denoted by $s \in (0,S)$. We denote with $\mathcal{D}(s)$ and $\partial\mathcal{D}(s)$ a cross section of $\Omega_\ominus$ and its boundary, respectively, and we assume that $\min |\D (s)| >0$, where $|\D (s)|$ is the measure of $\D (s)$. 
%In what follows, we assume for simplicity of notation that $\Sigma$ has a constant cross section, but this is not a restriction of the approach. 
We also assume that $\Omega_\ominus$ crosses $\Omega$ from side to side and we call $\Gamma$ the lateral (cylindrical) surface of $\Omega_\ominus$, while the upper and lower side faces of $\Omega_\ominus$ belong to $\partial\Omega$. We refer to Figure \ref{fig1} for an illustration of the notation.

@@

The objective of this work is to derive and analyze a simplified version of problem \eqref{eq:dirneu}, where the domain $\Omega_\ominus$ shrinks to its centerline $\Lambda$ and the corresponding partial differential equation is averaged on the cylinder cross section, namely $\mathcal{D}$. This new problem setting will be called the \emph{reduced} problem. Form the mathematical standpoint it is more challenging than \eqref{eq:dirneu}, because it involves the coupling of 3D/1D elliptic problems.
For the model reduction process, we decompose integrals as follows, for any sufficiently regular function $w$,
\begin{equation*}
\int_{\Omega_\ominus} w d\omega 
= \int_\Lambda \int_{\mathcal{D}} w d\sigma ds
= \int_\Lambda |\mathcal{D}|\avrd{w} ds\,,
\quad
\int_{\Gamma} w d\sigma 
= \int_\Lambda \int_{\partial\mathcal{D}} w d\gamma ds
= \int_\Lambda  |\partial \mathcal{D}| \avrc{w} ds\,,
\end{equation*}
where $\avrd{w}, \ \avrc{w}$ denote the following mean values respectively,
\begin{equation*}
\avrd{w} = |\mathcal{D}|^{-1} \int_{\mathcal{D}} w d\sigma\,,
\quad
\avrc{w} = |\partial\mathcal{D}|^{-1} \int_{\partial\mathcal{D}} w d\gamma\,.
\end{equation*}

@@

Using a model reduction approach based on averaging, we end up with two different formulations of a reduced problem
for the unknown $u$ defined on the entire 3D domain $\Omega$, coupled with the unknown $\ud$, defined on the 1D manifold $\Lambda$
and a Lagrange multiplier defined either on $\Gamma$ (problem 1) or on $\Lambda$ (problem 2). 
The scope of this work is to compare them, with the aim to determine which is the most suitable to set up a computational model for 3D-1D coupled PDEs.

@@

We apply the averaging technique to equation \eqref{eq:dirneu2}. In particular, we consider an arbitrary portion $\mathcal{P}$ of the cylinder $\Omega_\ominus$, with lateral surface $\Gamma _{\mathcal{P}}$ and bounded by two perpendicular sections to $\Lambda$, namely $\mathcal{D}(s_1), \ \mathcal{D}(s_2)$ with $s_1<s_2$. We have,
\int_{\mathcal{P}} -\Delta \uf + \uf d\omega =
-\int_{\partial \mathcal{P}} \nabla \uf \cdot \nn_{\ominus} \, d\sigma  + \int_{\mathcal{P}}\uf d\omega=
 \int_{\mathcal{D}(s_1)} \partial_s \uf d\sigma -  \int_{\mathcal{D}(s_2)} \partial_s \uf d\sigma -  \int_{\Gamma_{\mathcal{P}}} \nabla \uf \cdot \nn_{\ominus} d\sigma +\int_{\mathcal{P}}\uf d\omega
By the fundamental theorem of integral calculus combined with the Reynolds transport Theorem, 
being $\nu$ the normal deformation of the boundary along $(0,S)$, we have,

@@

 (d_s \ud, d_s \vd)_{\Lambda,|\mathcal{D}|} 

@@

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
\subsubsection*{Topological model reduction of the problem on $\Omega_{\oplus}$}
We focus here on the subproblem of \eqref{eq:dirneu1} related to $\Omega_{\oplus}$.
We multiply both sides of \eqref{eq:dirneu1} by a test function $v\in H^1_0(\Omega)$ and integrate on $\Omega_\oplus$. Integrating by parts and using boundary and interface conditions, we obtain
\begin{equation*}
\begin{split}
\int_{\Omega _{\oplus}}fv\,d\omega&=
\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\omega -\int _{\partial \Omega _{\oplus}}\nabla \up \cdot \nn_{\oplus} v\,d\sigma + \int_{\Omega_{\oplus}} \up v
\\
&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega -\int_{\Gamma} \nabla \up \cdot \nn_{\oplus} v + \int_{\Omega_{\oplus}} \up v
\\
&=\int _{\Omega _{\oplus}}\nabla \up \cdot\nabla v\,d\Omega +\int_{\Gamma} \lambda v + \int_{\Omega_{\oplus}} \up v.
\end{split}
\end{equation*} 
Then, we make the following modelling assumptions:
\begin{description}
\item[A2] we identify the domain $\Omega_{\oplus}$ with the entire $\Omega$, 
and we correspondingly omit the subscript $\oplus$ to the functions defined on $\Omega_{\oplus}$,
namely
\begin{equation*}
\int_{\Omega_{\oplus}} u_\oplus\, d\omega \simeq \int_{\Omega} u\, d\omega\,.
\end{equation*}
\end{description}
Therefore, we obtain 
\begin{equation*}
(\nabla u ,\nabla v)_{\Omega} +(u,v)_{\Omega}+(\lambda, v)_{\Gamma}  =(f,v)_{\Omega}
\end{equation*}
and combining with \eqref{eq:1Ddirneu_weak} we obtain the first formulation of the reduced problem.

\subsubsection*{Problem 1 (3D-1D-3D)}
Let $\langle \cdot , \cdot \rangle_\Gamma$ denote the duality pairing between 
$H^\frac12_{00}(\Gamma)$ and $H^{-\frac12}(\Gamma)$. The problem consists to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \lambda \in H^{-\frac12}(\Gamma )$, such that
\begin{subequations}\label{eq:problem1}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+ \langle \trace v  - \ext \vd, \lambda \rangle_\Gamma
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},\vd)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1(\Lambda)
\\
&   \langle \trace u - \ext \ud , \mu \rangle_\Gamma = 0
\quad \forall \mu \in H^{-\frac12}(\Gamma)\,.
\end{align}
\end{subequations}
Here, $\trace:H^1_0(\Omega) \rightarrow H^{\frac 12}_{00}(\Gamma)$ denotes the trace operator from $\Omega$ to $\Gamma$ and $\ext: H^1_0(\Lambda) \rightarrow H^1_{0}(\Gamma)$ denotes the uniform extension from $\Lambda$ to $\Gamma$.

% >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
Now, we apply a topological model reduction of the interface conditions, namely we go from a 3D-1D-2D formulation
involving sub-problems on $\Omega$ and $\Lambda$ and coupling operators defined on $\Gamma$
to a 3D-1D-1D formulation where the coupling terms are set on $\Lambda$. 
To this purpose, let us write the Lagrange multiplier and the test functions on every cross section $\partial\mathcal{D}(s)$ as their average plus some fluctuation,
\begin{equation*}
\lambda=\avrc{\lambda}+\tilde{\lambda}, \qquad v=\avrc{v}+\tilde{v},
\quad \text{on} \ \partial\mathcal{D}(s)\,,
\end{equation*}
where $\avrc{\tilde{\lambda}}=\avrc{\tilde{v}}=0$. 
Therefore, the coupling term on $\Gamma$ can be decomposed as,
\begin{equation*}
\int_{\Gamma}\lambda v\, d\sigma
=\int _{\Lambda}  \int_{\partial\mathcal{D}(s)} (\avrc{\lambda}+\tilde{\lambda})(\avrc{v}+\tilde{v})d\gamma ds
= \int_{\Lambda}|\partial\mathcal{D}(s)| \avrc{\lambda}\avrc{v}\,ds+\int_{\Lambda}  \int_{\partial\mathcal{D}(s)} \tilde{\lambda}\tilde{v}d\gamma ds\,.
\end{equation*}

@@

\subsection{Problem 2 (3D-1D-1D)}
Let $\langle \cdot , \cdot \rangle_\Lambda$ denote the duality pairing between 
$H^\frac12_{00}(\Lambda)$ and $H^{-\frac12}(\Lambda)$.
The problem requires to find $u \in H^1_0(\Omega),\ \ud \in H^1_0(\Lambda), \ \ld \in H^{-\frac12}(\Lambda)$, such that
\begin{subequations}\label{eq:problem2}
\begin{align}
&(u,v)_{H^1(\Omega)} + (\ud,\vd)_{H^1(\Lambda),|\D|} 
+  \langle \mtrace v - \vd, \ld \rangle_{H^{-\frac12}(\Lambda), |\DD|} 
\\
\nonumber
&\qquad\qquad= (f,v)_{L^2(\Omega)} +  (\avrd{g},V)_{L^2(\Lambda),|\D|}
\quad \forall v \in H^1_0(\Omega), \ \vd \in H^1_0(\Lambda)\,,
\\
&   \langle \mtrace u -   \ud, \md \rangle_{H^{-\frac12}(\Lambda),|\DD|} = 0
\quad \forall \md \in H^{-\frac12}(\Lambda)\,,
\end{align}
\end{subequations}
where $\mtrace$ denotes the composition of operators $\trace \circ \avrc{(\cdot)}$.
We notice that all the integrals of the reduced problem are well defined because 
$\mtrace: H^1_0(\Omega) \rightarrow H^\frac12_{00}(\Lambda)$ as shown in the following lemma.

%\begin{lemma}\label{lemma:H12norm}
%{\color{red}TO DO: generalize to not uniform $\DD$} 
%When $\Gamma$ is a cylinder, if $u\in H_{00}^{\frac 12}(\Gamma)$, then $\avrc{u}\in H_{00}^{\frac 12}(\Lambda)$. Moreover, if $u\in H^{\frac 12}_{00}(\Gamma)$ is constant on each cross section, namely $u(s,\theta)=u(s)$, then 
%\begin{equation*}
%\|u\|_{H^{\frac 12}_{00}(\Gamma)}=2\pi R \|u\|_{H^{\frac 12}_{00}(\Lambda)}.
%\end{equation*}
%\end{lemma}
%\begin{proof}
%Let us denote as $\phi _{ij}$ and $\rho _{ij}$, for $i=1,2,\dots$, $j=0,1,\dots$, the eigenfunctions and the eigenvalues of the laplacian on $\Gamma$, and with $\phi _i$ and $\rho _i$ the eigenfunctions and the eigenvalues of the laplacian on $\Lambda$. In particular,
%\begin{align*}
%\phi _{ij}(s,\theta)=sin (i\pi s)\left( cos(j\theta)+ sin(j\theta) \right),\\
%\rho_{ij}=i\pi ^2+\frac{j^2}{R^2},\\
%\phi _{i}(s)=sin (i\pi s),\\
%\rho _i = i\pi ^2.
%\end{align*}
%It is easy to verify that 
%\begin{eqnarray}
%\label{null_int_eigenf}
%\int_0^{2\pi} \phi _{ij}(s,\theta)=0 \quad \forall j>0, \forall i \\
%\label{nonull_int_eigenf}
%\int_0^{2\pi} \phi _{ij}(s,\theta)= 2\pi R \, \sin(i \pi s) \quad \mbox{if } j=0, \forall i  .\\
%\end{eqnarray}
%Moreover we recall that $\phi_{i,j}(s,\theta)$ and $\phi _i(s)$ are orthogonal basis of $L^2(\Gamma)$ and $L^2(\Lambda)$ respectively. Therefore,
%\begin{multline*}
%\avrc{u}(s)=\frac{1}{2\pi R}\int_0^{2\pi} u(s,\theta)R\, d\theta
%= \frac{1}{2\pi R}\int_0^{2\pi} \sum_{i,j} a_{i,j} \phi_{i,j}(s,\theta) R\, d\theta
%\\= \frac{1}{2\pi R}\sum_{i,j} a_{i,j}\int_0^{2\pi}  \phi_{i,j}(s,\theta) R\, d\theta
%=  \sum_{i} a_{i,0} \phi_{i}(s).
%\end{multline*}
%From \cite[Lemma 4.11]{chandler2015interpolation} we have
%\begin{equation}\label{H12norm_Gamma}
%\|u\|^2_{H^{\frac 12}(\Gamma)}=\sum_{i=1}^{\infty}\sum_{j=0}^{\infty} \left( 1+ \rho_{ij}\right)^{\frac 12}|a_{ij}|^2,
%\text{ with }
%a_{ij}=\int _0^1\int _0^{2\pi} u(s,\theta )\phi_{ij}\, R d\theta ds.
%\end{equation}
%and 
%\begin{equation*}
%\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=\sum_{i=1}^{\infty} \left( 1+ \rho_{i}\right)^{\frac 12}|\avrc{a}_i|^2,
%\text{ with }
%\avrc{a}_i=\int _0^1 \avrc{u}(s )\phi_{i}(s) ds.
%\end{equation*}
%
%Therefore, we have
%\begin{multline*}
%\|\avrc{u}\|^2_{H^{\frac 12}(\Lambda)}=
%\sum_{i=1}^{\infty}\left( 1+ i^2\pi^2\right)^{\frac 12}\left( \int_0^1 \avrc{u}(s) sin(i\pi s)\, ds \right)^2\\
%= \sum_{i=1}^{\infty} \left( 1+ i^2\pi^2\right)^{\frac 12}\left( \sum_{j=1}^\infty a_{j,0}\int_0^1 \sin(j\pi s) \sin(i\pi s) \, ds  \right)^2\\
%= \sum_{i=1}^{\infty} \frac 14 \left( 1+ i^2\pi^2\right)^{\frac 12}a_{i,0}^2\\
